Conditional selectivity for Hexastores

### 2012-09-06 conditional/trunk/selectivity-basic.tex
Rename paper
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@357 43ef1190-90fd-4dd7-a769-d0121f02b80e

A very simple example is to find the selectivity for the triple pattern
\begin{verbatim}
?person a foaf:Person .
\end{verbatim}
We can easily see that $sel(T) = 2/7$ since two out of the 7 triples
match the pattern. To see how Eq.~\ref{eq:sel} is used, we note that
$sel(S) = 1$ since it is a variable. $sel(P | S) = 2/7$ since the
predicate matches the two occurences of \rdfterm{rdf:type} and the
subject variable doesn't influence this. Finally, $sel(O | S \cap P) =
1$ since the only two occurences of \rdfterm{foaf:Person} occurs in
the same triples as \rdfterm{rdf:type}. Thus, we arrive at the
expected result.

>>>>

A very simple example is to find the selectivity for the triple pattern
\begin{verbatim}
?person a foaf:Person .
\end{verbatim}
We can easily see that the correct answer is $sel(T) = 2/7$ since two
out of the 7 triples match the pattern. To see how Eq.~\ref{eq:sel} is
used, we note that $sel(S) = 1$ since it is a variable. $sel(P | S) =
2/7$ since the predicate matches the two occurences of
\rdfterm{rdf:type} and the subject variable doesn't influence
this. Finally, $sel(O | S \cap P) = 1$ since the only two occurences
of \rdfterm{foaf:Person} occurs in the same triples as
\rdfterm{rdf:type}. Thus, we arrive at the expected result.
